### 2022-03-23 src/text/2-package.tex
Changed subsection order and add label in datasets
add maps section
Run tex indentation
Fix input references
First addition of workflow part

\section{Analysis Workflow Overview}
\label{sec:analysis-workflow-overview}

@@

\todo{How to sort the sub-packages? After data flow or alphabetically?}
\input{text/2-package-subsections/analysis}
\input{text/2-package-subsections/astro}
\input{text/2-package-subsections/catalog}
\input{text/2-package-subsections/data}
\input{text/2-package-subsections/datasets}
\input{text/2-package-subsections/estimators}
\input{text/2-package-subsections/irf}
\input{text/2-package-subsections/makers}
\input{text/2-package-subsections/modeling}
\input{text/2-package-subsections/stats}
\input{text/2-package-subsections/utils}
\input{text/2-package-subsections/visualisation}

>>>>

\section{Analysis Workflow Overview}
\label{sec:analysis-workflow-overview}
\todo{Regis and Fabio F.}

\subsection{Data access and selection (DL3)}

The analysis of gamma-ray data with Gammapy starts at the Data Level 3 where the data consists
in lists of gamma-like events and their corresponding instrument response functions (IRFs).
The latter include effective area, point spread function (PSF), energy dispersion and
residual hadronic background. In addition there is associated meta data including information
on the observation such as pointing direction, observation time and observation conditions.

\subsection{Data reduction (DL3 to DL4)}

In the next stage of the analysis the user selects a coordinates system, region or
energy binning and events are binned into multidimensional data structures (maps)
with the selected geometry. The instrument response is projected onto the
same geometry as well. At this stage users can select additional background
estimation methods, such as ring background or reflected regions and
exclude parts of the data with high associated IRF systematics by defining
a "safe" data range. The counts data and the reduced IRFs are bundled into
datasets. Those datasets can be optionally grouped and stacked and are
typically written to disk to allow users to read them back at any time later
for modeling and fitting.

@@

\todo{How to sort the sub-packages? After data flow or alphabetically? What
	about maps?}
\input{text/2-package-subsections/data}
\input{text/2-package-subsections/irf}
\input{text/2-package-subsections/maps}
\input{text/2-package-subsections/makers}
\input{text/2-package-subsections/datasets}
\input{text/2-package-subsections/modeling}
\input{text/2-package-subsections/stats}
\input{text/2-package-subsections/estimators}
\input{text/2-package-subsections/analysis}
\input{text/2-package-subsections/visualisation}
\input{text/2-package-subsections/astro}
\input{text/2-package-subsections/catalog}
\input{text/2-package-subsections/utils}
